Creation of a DRN shapefile with associated capacities

### 2022-03-22 R/Core_code/DRN_operations/DRN_processing.Rmd
update repo and drn_processing

```{r}
writeOGR(glob_wat_cut, dsn = "./Global_surface_water", layer = "global_wat_cut",
         driver = "ESRI Shapefile" )
```

@@

```{r load DRN to update}
DRN_update <- readOGR(dsn = "./DRN/DRN_update_area_ID.shp")
```

@@

#Export the updated DRN
# writeOGR(DRN_update,dsn = "./DRN", layer = "DRN_afterR_v1",
#          driver = "ESRI Shapefile")
```

@@

#Export the updated DRN
# writeOGR(DRN_update,dsn = "./DRN", layer = "DRN_afterR_v2",
#          driver = "ESRI Shapefile" )
```

@@

#Load the updated DRN
#Method 1 (Unidentified reservoirs associated to the lowest class)
# path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/DRN/DRN_afterR_v1.shp"
#Method 2 (Unidentified reservoirs removed)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/DRN/DRN_afterR_v2.shp"

@@

#Dataframe creation: first column SubbasinID, others number of reservoirs in the classes
path<-"C:/Thesis_fortran/WASA/shapefile/Banabuiu"
subbasins<-st_read(paste0(path,"/subbasins_cut.shp"))
count_class <- subbasins %>%
                filter(!is.na(SubbasinID)) %>%
                group_by(SubbasinID) %>%
                summarize()
count_class <- data.frame(count_class$SubbasinID)
names(count_class) <- "SubbasinID"

for(i in 1:5){
  if(i != 1){
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(count=n())
  }else{
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i]) %>%
          summarize(count=n())
  }
  for(a in seq_len(length(c$SubbasinID))){
    for(b in seq_len(length(count_class$SubbasinID))){
        if(c$SubbasinID[a] == count_class$SubbasinID[b]) count_class[b,i+1] <- c$count[a]
    }
  }
}
names(count_class) <- c("SubbasinID","class1","class2","class3","class4","class5")
count_class[is.na(count_class)] <- 0

#Class ripartition
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
count_class<-read.table(paste0(path, "/lake_number_newDRN_met2.dat"), skip = 2)

for(i in 2:6){
  print(paste0("Percentage of resevoirs in Class ",i-1))
  print(paste0(round(sum(count_class[,i])/sum(count_class[,2:6]),digits = 3)*100," %"))
}
```

@@

```{r lake.dat}
#Create the dataframe
par_class<-data.frame(seq(1,5,1),     #Reservoir_class-ID
                      round(res_class,2),      #maxlake0
                      rep(1,5),       #lake_vol0_factor
                      rep(0,5),       #lake_change: this parameter can be changed in the calibration phase
                      rep(alpha_Molle,5),   
                      rep(damk_Molle,5),
                      c(12.5,18.75,25,37.5,50),       #damc_hrr
                      rep(1.5,5)      #damd_hrr
                      )
names(par_class)<-c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")
View(par_class)

#Save it
options(scipen = 999)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(par_class,file=paste0(path,"/lake.dat"),
         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
options(scipen = 0)
```

@@

```{r lake_number}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(count_class,file=paste0(path,"/lake_number_newDRN_met2.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
```

@@

```{r representative reservoirs}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis"
res<-read.table(paste0(path,"/reservoir_name_ID.txt"), header = TRUE, sep = "\t")

median_class<- data.frame(res$SubbasinID)
names(median_class) <- "SubbasinID"

for(i in 1:5){
  if(i != 1){
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(median(capacity))
  }else{
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i]) %>%
          summarize(median(capacity))
  }
  for(a in 1:length(c$SubbasinID)){
    for(b in 1:length(median_class$SubbasinID)){
        if(c$SubbasinID[a]==median_class$SubbasinID[b]) median_class[b,i+1]<-c$`median(capacity)`[a]
    }
  }
}
names(median_class)<-c("SubbasinID","class1","class2","class3","class4","class5")
median_class[is.na(median_class)]<-0
```

```{r export lake_maxvol}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(round(median_class,2),file=paste0(path,"/lake_maxvol_newDRN_m2_median.dat"),
         header = "Specification of water storage capacity for the reservoir size classes\nSub-basin-ID, maxlake[m**3] (five reservoir size classes)",f = write.table)
```

@@

```{r no DRN lake}
#Dataframe construction
par_class<-data.frame(seq(1,5,1),     #Reservoir_class-ID
                      round(res_class,2),      #maxlake0
                      rep(1,5),       #lake_vol0_factor
                      rep(0,5),       #lake_change: leave it to 0, so the number of reservoirs doesn't increase
                      rep(alpha_Molle,5),   
                      rep(damk_Molle,5),
                      c(12.5,18.75,25,37.5,50),       #damc_hrr
                      rep(1.5,5)      #damd_hrr
                      )
names(par_class)<-c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")

#Save it
options(scipen = 999)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(par_class,file=paste0(path,"/lake_noDRN.dat"),
         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
options(scipen = 0)
```

@@

#No reservoirs
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
write.table("Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",paste0(path,"/lake_number_noDRN_v1.dat"), row.names = FALSE, quote = FALSE, col.names = FALSE)

#Only one resevoir in the smallest reservoir class
count_class[,2]<-1
count_class[,3:6]<-0
my.write(count_class,file=paste0(path,"/lake_number_noDRN_v2.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)

#Only zeros
#it works!!!!
count_class[,2]<-0
count_class[,3:6]<-0
my.write(count_class,file=paste0(path,"/lake_number_noDRN_v3.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)

```

>>>>

```{r}
writeOGR(glob_wat_cut, dsn = "./Data/DRN/Global_surface_water", layer = "global_wat_cut",
         driver = "ESRI Shapefile")
```

@@

```{r load DRN to update}
DRN_update <- readOGR(dsn = "./Data/DRN/DRN_update_area_ID.shp")
```

@@

#Export the updated DRN
writeOGR(DRN_update, dsn = "./DRN", layer = "DRN_afterR_v1",
          driver = "ESRI Shapefile")
```

@@

#Export the updated DRN
writeOGR(DRN_update, dsn = "./DRN", layer = "DRN_afterR_v2",
          driver = "ESRI Shapefile")
```

@@

#Load the updated DRN
#Method 1 (Unidentified reservoirs associated to the lowest class)
# path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/DRN/DRN_afterR_v1.shp"
#Method 2 (Unidentified reservoirs removed)
path <- "./Data/DRN/DRN_afterR_v2.shp"

@@

#Dataframe creation: first column SubbasinID, others number of reservoirs in the classes
subbasins <- st_read("./Data/Shapefile/subbasins_cut_geomfix.shp")
count_class <- subbasins %>%
                filter(!is.na(SubbasinID)) %>%
                group_by(SubbasinID) %>%
                summarize()
count_class <- data.frame(count_class$SubbasinID)
names(count_class) <- "SubbasinID"

for(i in 1:5){
  if(i != 1){
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(count=n())
  }else{
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          filter(capacity < res_class[i]) %>%
          summarize(count = n())
  }
  for(a in seq_len(length(c$SubbasinID))){
    for(b in seq_len(length(count_class$SubbasinID))){
        if(c$SubbasinID[a] == count_class$SubbasinID[b]) count_class[b,i+1] <- c$count[a]
    }
  }
}
names(count_class) <- c("SubbasinID", "class1", "class2", "class3", "class4", "class5")
count_class[is.na(count_class)] <- 0

#Class ripartition
for(i in 2:6){
  print(paste0("Percentage of resevoirs in Class ", i-1))
  print(paste0(round(sum(count_class[,i])/sum(count_class[,2:6]),digits = 3)*100," %"))
}
```

@@

```{r lake.dat}
#Create the dataframe
par_class <- data.frame(seq(1,5,1),     #Reservoir_class-ID
                        round(res_class,2),      #maxlake0
                        rep(1,5),       #lake_vol0_factor
                        rep(0,5),       #lake_change: this parameter can be changed in the calibration phase
                        rep(alpha_Molle,5),
                        rep(damk_Molle,5),
                        c(12.5,18.75,25,37.5,50),       #damc_hrr
                        rep(1.5,5)      #damd_hrr
                       )
names(par_class) <- c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")
View(par_class)

#Save it
options(scipen = 999)
path <- "./Data/Scenarios/AR"
my.write(par_class, file = paste0(path, "/lake.dat"),
         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",
         f = write)
options(scipen = 0)
```

@@

```{r lake_number}
path <- "./Data/Scenarios/AR"
my.write(count_class, file = paste0(path,"/lake_number.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",
         f = write)

#Check class ripartition
path <- "./Data/Scenarios/AR"
count_class <- read.table(paste0(path, "/lake_number.dat"), skip = 2)
```

@@

```{r lake_maxvol}
path <- "./Data/General"
res <- read.table(paste0(path, "/reservoir_name_ID.txt"), header = TRUE, sep = "\t")

median_class <- data.frame(res$SubbasinID)
names(median_class) <- "SubbasinID"

for(i in 1:5){
  if(i != 1){
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(median(capacity))
  }else{
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i]) %>%
          summarize(median(capacity))
  }
  for(a in seq_len(length(c$SubbasinID))){
    for(b in seq_len(length(median_class$SubbasinID))){
        if(c$SubbasinID[a]==median_class$SubbasinID[b]) median_class[b,i+1]<-c$`median(capacity)`[a]
    }
  }
}
names(median_class) <- c("SubbasinID","class1","class2","class3","class4","class5")
median_class[is.na(median_class)] <- 0
```

```{r export lake_maxvol}
path <- "./Data/Scenarios/AR"
my.write(round(median_class,2), file=paste0(path, "/lake_maxvol.dat"),
         header = "Specification of water storage capacity for the reservoir size classes\nSub-basin-ID, maxlake[m**3] (five reservoir size classes)",
         f = write)
```

@@

```{r no DRN lake}
#Dataframe construction
par_class <- data.frame(seq(1,5,1),     #Reservoir_class-ID
                       round(res_class, 2),      #maxlake0
                        rep(1,5),       #lake_vol0_factor
                        rep(0,5),       #lake_change: leave it to 0, so the number of reservoirs doesn't increase
                        rep(alpha_Molle, 5),   
                        rep(damk_Molle, 5),
                        c(12.5,18.75,25,37.5,50),       #damc_hrr
                        rep(1.5, 5)      #damd_hrr
                        )
names(par_class) <- c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")

#Save it
options(scipen = 999)
path <- "./Data/Scenarios/LR"
my.write(par_class, file=paste0(path, "/lake.dat"),
         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",
         f = write)
options(scipen = 0)
```

@@

#No reservoirs
path <- "./Data/Scenarios/LR"
#Only zeros
count_class[, 2] <- 0
count_class[, 3:6] <- 0
my.write(count_class,file = paste0(path, "/lake_number.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",
         f = write.table)
```
